---
title: "Coaseian Tunas - Incentives Based Programs for the Successful Governance of Wild Ocean Fisheries"
author: "Dan Ovando, Gary Libecap, Cody Wilgus"
date: "ECON 260 March 11, 2016"
output:
  pdf_document:
    toc: yes
    fig_caption: yes
    fig_width: 5
    fig_height: 5
fontsize: 12pt
number_sections: yes
csl: fish-and-fisheries.csl
bibliography: Coaseian Tunas.bib
---

## Introduction

As social animals, humans have developed an wide portfolio of strategies for sharing limited resources, from facial expressions to the Federal Reserve. Common-pool resources (CPRs) have proved to be an enduring challenge for humanity though; when exclusion is difficult and goods rivalrous, we have repeatedly seen poor outcomes arise. CPRs are unfortunately especially common in the natural environment, and the fingerprints of their special challenges can be seen in the rise and persistence of problems as diverse as climate change, water scarcity, deforestation, and overfishing.

Hardin [-@Hardin1968] would suggest that these outcomes are inevitable without "mutual coercion, mutually agreed upon", by which we may interpret his meaning as a requirement for laws to designed to prevent our selfish natures from depleting CPRs. Ostrom provides us with some cause for optimism though; her work points out that under the right circumstances (broadly, low transaction cost settings) humans can solve CPR problems through collective action [@Ostrom1994; @Ostrom1990; @Ostrom2000].

While the works of Ostrom provide us with a clearer picture of human behavior, it does seem that Hardin's more pessimistic vision is justified in more complex settings, where the collective actions supported by Ostrom are unlikely to develop. In these circumstances, Pigouvian taxes have been commonly prescribed as the solution; If we desire less pollution, we should simply find the rate at which to tax the polluter such that the optimal level of pollution is achieved.

While this Pigouvian strategy has been commonly applied, and has arguably been successful in many instances, Coase [-@Coase1960] suggests that there may be a better way. A Pigouvian approach ignores the fact that there are two sides to every tax; a benefit to one party may be a cost to another. A tax-based approach also presumes the ability of a central planner to set a tax rate in order to achieve objectives, which may differ from the objectives of affected parties.  Coase suggests that by assigning property rights, if transaction costs are low affected parties will achieve an optimal allocation of resources; the polluter and pollutee can use the market to arrive at a desired balance of costs and benefits. This simple solution becomes much more complicated when transaction costs rear their ugly heads, but by focusing on incentives Coase's general point provides a powerful solution to CPR problems.

Together then, these authors provide a wealth of tools for diagnosing the cause, and potential solutions, to CPR problems. When we observe an environmental problem, we can use this literature to consider why that problem may persist, and what remedies may be most effective. Is an observed issue potentially solved by collective action if enforceable borders can be put in place? Can application or property rights allow market solutions? Are transaction costs too high, and how can they be reduced?

We apply this paper to the persistent problem of overfishing of Bigeye tuna (*Thunnus obesus*) in the Western-Central Pacific Ocean (WCPO). We ask: Why does the Bigeye tuna fishery remain overfished, and might a Coaseian approach provide a solution? Our focus is on the potential of bycatch reduction to achieve these goals, rather than reform of the Bigeye fishery itself.

## Background

The latest stock assesment for Bigeye tuna [@Harley2014] indicates that the stock has been experiencing overfishing for several years, though biomass levels have yet to fall commensurately. There is strong evidence that current levels of fishing are unsustainable, and changes will need to be made to ensure the future viability of the fishery and population. While this fact is in little question, few successful steps have been take to reduce Bigeye fishing mortality. This is largely due to imbalances in costs and benefits. Bigeye are primarily targeted by long-line and pole-and-line fisheries supplying the lucrative Asian sashimi market. Roughly 50% of the total catch of Bigeye comes from these targeted fisheries [@Harley2014]. However, the other ~50% of Bigeye catch comes through primarily juvenile incidental bycatch in the Skipjack tuna (*Katsuwonus pelamis*) fishery. As such, the Bigeye interest in the fishery have little incentive to conserve, since they believe conservation efforts will be offset by the effects of the Skipjack bycatch, while the Skipjack fleet has little incentive to further reduce Bigeye bycatch since they receive little benefit from such actions.

### Bigeye Biology

Bigeye tuna are a fast growing tuna species distributed throughout tropical and subtropical waters of the Pacific Ocean [@Harley2014]. While they exhibit some site fidelity, their wide movement range results in little evidence of genetic substocks throughout the species' range. As a result, the Bigeye fishery is a prime example of a difficult CPR problem, as it represents a biological stock covering thousands of miles and crossing numerous Exclusive Economic Zones (EEZs). Adult Bigeye often move rapidly in conjunction with schools of dolphins, feeding on other fish and small crustaceans. Juvenile Bigeye are less mobile, and as such are especially attracted to floating objects where they take refuge and feed. Bigeye undergo dial migrations from deep waters during daylight hours to shallower at night

However, Bigeye's also have numerous traits that should defend them from overfishing [@Harley2014]. They grow quickly to their maximum size of ~2 meters, and reach sexual maturity within 2-3 years. They have relatively high natural mortality (~0.5, though this value changes with age), indicating a life history evolved to deal with high mortality rates, which as such can often sustain heavier fishing. Bigeye are also believed to have a relatively flat spawner-recruit relationship, indicating that the population can maintain high levels of recruitment even when the spawning population has been greatly reduced. Skipjack tuna are smaller, faster growing, and shorter lived than bigeye. They are also surface schooling, placing them often in cohort with juvenile bigeye.

### Fisheries

We describe the general history, management context, and economic state of the Bigeye and Skipjack fisheries

#### Management Context

Both Skipjack and Bigeye are managed by the Western and Central Pacific Fisheries Commission (WCPFC). The WCPFC was put into place in 2004, and has approximately 14 member states with vested interests in Skipjack and/or Bigeye [@Hanich2012]. The WCPFC has a Scientific Committee charged with providing advice on stock status and tested management recommendations. However, the member states must vote on the structure of the actual regulations, and are not bound to the recommendations of the Scientific Committee in the manner of many US fisheries. Management actions include restrictions on gear, effort, spatial restrictions, and some limited attempts at catch restrictions.

Member states can also restrict access through the sale of fishing days to distant water fleets (DWFs). This is especially common among the Pacific Island Nations (PINs) making up the WCPFC. So, a PIN can decide on a number of fishing days it would like to allocated within its EEZ, and sell those days to foreign fleets, such as those from Japan and the USA.

#### Bigeye Fishery

Bigeye are primarily targeted by long-line vessels for the Asian sashimi market. Prices can reach near $10 kg [@Kompas2010]. These include near shore fleets around Taiwan (Chinese-Taipei), Indonesia, the Philippines, Papua New Guinea, the Solomon Islands, and Vietnam, and DWFs from Japan, Korea, Taiwan, and China operating along the Eastern portions of the region. Most of the catch comes from Japan and Taiwan, though small-scale coastal catches by Indonesia have been increasing. Almost 50% of Bigeye catches are caught as bycatch in the Skipjack fishery.

Bigeye tuna began experiencing overfishing in the 2000s. At first, this overfishing was attributed to excessive targeting by long-liners, but subsequent assessments attributed a substantial portion of the blame on bycatch of juveniles in the Skipjack fishery [@Harley2014]. This overfishing has yet to drive down the population size, but if the models are correct current levels of fishing mortality are unsustainable.

#### Skipjack Fishery

Skipjack make up the bulk of tuna catches in the WCPO, and are caught almost entirely be purse seiners using Fish Aggregating Devices (FADs).These FADs have made large scale fishing operations in the open ocean much more viable, as vessels can deploy and track FADs, allowing them to "know" with much greater certainty where tuna will be. Skipjack are primarily canned and sold to the USA, EU, and Japan for ~$1-2/kg [@Kompas2010]. These FADs also act to concentrate smaller and less mobile juvenile Bigeye, contributing to the Bigeye bycatch problem. Purse seining is primarily operated by Papua New Guinea, Kiribati, Tuvalu, Nauru, Federated States of Micronesia and the Solomon Islands, either directly through fishing or through leasing of vessel days. The USA also has a substantial DWF interest in Skipjack.

Despite increasing effort in recent years, the Skipjack fishery remains in relatively good condition, with both very high biomass and relatively low fishing mortality rates. Current fishing levels are likely to maintain the stock near its current size, and even expanded fishing effort would likely not drive the population below B~MSY~ [@Rice2014].

## Solutions

Given this context then, what can be done to improve the status of Bigeye tuna? The broader goal of the project is to explore Coaseian exchange solutions. However, it is instructive, especially in the light of this class, to consider other potential solutions and why a Coaseian approach may be the most practical.

We begin acknowledging that we seem to be heading to a Hardin-esque path, in which international players race to the commons to exploit the bigeye. Given that Hardin's predictions seem accurate in this context, what about Hardin's solutions? Hardin might suggest a legislative solution, whereby we impose regulations to limit our collective behavior. This approach seems to have worked somewhat for other Tunas in the region (Fig.1). However, we can say that we have already tried a regulatory approach in the Bigeye fishery, and yet these regulations have not worked, as stakeholders have not set regulations at ideal levels. As such, we must turn our attention to other solutions.

![Kobe plot of global tuna stocks](tuna_kobe_plot.tiff)

### Collective Action

Let us begin with Ostrom. Might collective action provide a solution to the over-exploitation of Bigeye? Given the scale of the stock, this may seem like a foolish concept. However, it is worth considering as an exercise in characterizing the challenges facing the Bigeye fishery. In addition, many of the PINs that target Bigeye have rich histories of collective action solutions to CPRs. So, it seems conceivable that these countries may be more amenable to the use of collective action solutions. Given that Ostrom provides such a clear framework for classifying the potential for collective action, we will work through her 8 principles.

*Clearly defined boundaries*. We are not off to a good start. Clearly the Bigeye tuna stock does not fall within clearly defined boundaries, unless one counts the mid Pacific Ocean basin. Bigeye move within and across the patchwork of EEZs, preventing clear distinctions of who has rights to access the resource, besides just about everybody in the region. Even within EEZs, where it could be argued the boundaries are better defined, given the large and maritime nature of the region enforcement becomes a major problem. As such, detecting and enforcing boundaries is very difficult even within EEZs. However, relative to other tuna stocks the WCPO's waters fall mostly within EEZs instead of high seas, which give at least some semblance of borders.

*Congruence with local conditions*. Bigeye fails this test as well. The huge biological range of the stock means that regulations set by WCPFC must be reflective of ocean-wide trends, rather than regional conditions. So, appropriation rules may be set that do not reflect local conditions. For example, PINs around which Bigeye concentrate may perceive a different, and more optimistic, stock status than a regional assessment body. In addition, while not an equilibrium problem, the current overfishing but not overfished status of the Bigeye stock poses a perception problem; it is much more difficult for users to perceive overfishing when the stock size has not yet been driven down to levels which reduce catcheability and yield per recruit. As such, there is little congruence between appropriation rules and local conditions.

*Collective Choice Arrangements*. Bigeye fares somewhat better here. Obviously every bigeye fishing boat does not have a direct say in management. But, the collective nature of the WCPFC does provide an avenue for collective choice. Each of the Bigeye fishing nations is able to express interests and help modify rules through the Commission. Therefore, there does appear to be potential for collective choice.

*Monitoring*. On the scale of pelagic fisheries, Bigeye does have relatively strong monitoring. Observers are present on most vessels, landing ports are monitored, landings tallied, etc. Few pelagic fisheries can boast similar conditions. However, while Bigeye may have strong monitoring for a pelagic stock, it is certainly not able to actively monitor and enforce effectively. The scale of operations is simply too large, and illegal fishing can and does occur. Monitoring then gets a mixed score.

*Graduated Sanctions*. The sanctions mechanisms within the WCPFC are somewhat unclear. There must be some penalties for violations of agreements, but it is unclear whether clear graduated sanctions exist.

*Conflict Resolution Mechanisms*. Deeper reading of the WCPFC management documents is needed to fully understand the conflict resolution mechanisms, but one can imagine that these mechanisms are not "rapid" and "low cost". Presumably, if one EEZ feels that a neighbor has violated some aspect of their Bigeye arrangement, they cannot simply walk next door and resolve the problem. They will likely have to go through a formal process with the Commission.

*Minimal recognition of rights to organize*. While the WCPFC provides a means for local constituents to organize and express their opinions, it also by definition must constrain them some. Final decisions are compromises among member states, and so doubtless on occasion regulations will clash with local institutional decisions.

*Nested Enterprise*. Bigeye seems to fail this test as well, as most of the institutions are concentrated within the WCPFC.

Taken together then, it is clear that we should not expect a collective action solution to Bigeye overfishing to arise. This again should perhaps not come as a surprise, but it is instructive to specifically consider why this is the case. The most significant violations of Ostrom's principles lie in the boundaries, monitoring, and ability of appropriation laws to match local conditions.

### Pigouvian Solutions

An alternative solution to outright regulation (the status quo) or collective action may be taxation. We could think of the bycatch of juvenile Bigeye as an externality imposed by the Skipjack fleet on the Bigeye stock and its associated vested interests (e.g. conservationists). So, one solution may be to simply internalize the cost of the Bigeye bycatch into the price of of Skipjack through a tax. Much in the same way that we have become accustomed to seeing "dolphin safe" logos, and their associated costs in gear changes and spatial avoidance, on cans of tuna, perhaps we could begin to see a "No Baby Bigeye" seal and tax on every can of Skipjack tuna.

To some extent, we may be seeing the development of such a change. A significant driver of the "Dolphin Safe" movement was market access; once the US placed restrictions on the import of tuna that did not conform to dolphin safe standards, many companies had to change their practices or risk losing substantial business. In many ways then this approximates a tax on non dolphin safe tuna. Skipjack has recently begun to lose market access at some retailers that place premiums on sustainability, due to its impact on the Bigeye stock. So, it will be interesting to see how this plays out, and what impact this loss of market share may do to Skipjack practices.

However, I am skeptical that the Bigeye issue will have the same transformative effect as the "Dolphin Safe" movement. It is difficult to imagine regulatory mandates at the national level for Bigeye, in the manner of dolphins, or consumer sentiment reaching the level engendered by marine mammals. So, we may perhaps see some improvement in practices from loss of market share, but likely further work will be needed.

If we likely cannot rely on a public-sentiment driven campaign for reduction of Bigeye bycatch, what about a decision by the WCPFC? Given their interest in the management of all tuna stocks in the WCPO, might they be able to enact a landing tax, or a tax on the purchase of vessel days within EEZs, in order to reduce Bigeye bycatch? More research is needed on the voting structure of the WCPFC, but it seems unlikely. Nearly every country represented has mixed interests in Bigeye and Skipjack. Therefore, one cannot imagine a country coming as a unified front to support a tax on Skipjack, and the WCPFC does not have a mechanism for unilateral actions.

At the end of the day, a tax on Skipjack would impose a cost on Skipjack and provide a benefit to Bigeye. Given the proper political incentives, this may well be an acceptable solution. However, under the voting structure of WCPFC and it seems unlikely that a sufficient number of players would vote against their own self interest, and indeed we have seen exactly that in the votes for effort caps and allocation. A vote for a restriction on effort is in some ways analogous to a vote for a tax increase, and we have seen a political inability among the WCPFC member states to voluntarily reduce effort in a manner sufficient to prevent the continued overfishing of Bigeye.

### Coaseian Solutions

If outright regulation, collective action, and taxes are unlikely to provide a solution to the overfishing of Bigeye, we must look elsewhere for a solution. For the remainder of this paper, we will consider a Coaseian solution to the overfishing of Bigeye tuna. Coase [@-Coase1960] points out that there are two sides to every deal: A tax on an externality imposes a cost on the party emitting the externality. This may be entirely reasonable in some cases. Under the Bigeye case here though, this imbalance of costs and benefits is likely inhibiting action.

A Coaseian solution then would appear as the following. We have two interests, Bigeye and Skipjack. Bigeye would benefit from reductions in bycatch by Skipjack, but Skipjack incurs a cost in order to make that reduction. Under the simplest Coaseian solution, if property rights are perfect and transaction costs are zero, Bigeye and Skipjack should be able to negotiate a an optimal level of Bigeye bycatch reduction given the the interests of each party. This seems like a logical solution to the Bigeye bycatch reduction problem. However, we clearly know (as did Coase) that these assumptions are not likely to hold in the real world, and certainly not in this case. Before considering the specifics of the potential Coaseian transaction proposed here, let us examine the two critical assumptions of property rights and zero transaction costs.

Beginning with transaction costs. There can be no doubt that transaction costs exist in this scenario. However, there is reason to believe that transaction costs are not necessarily inhibitive to a Coaseian bargain in this case. We can envision a number of transaction costs in this scenario. There may be information costs, in both the acquisition of information on the status of the stock, and in asymmetric information among participants.

However, the WCPFC already runs stock assessments for both the Skipjack and Bigeye stocks on a regular basis [@Harley2014; @Rice2014a]. While there are clearly uncertainties in the assessment, even under the status quo we already have fairly accurate data on the status of the stock. There also does not appear to be substantial controversy regarding stock status. So, there do not appear to be significant new transaction costs associated with information on stock status inhibiting a Coaseian bargain. The available stock assessments already provide information on the recommended reductions of catch of targeted Bigeye, and Bigeye bycatch in the Skipjack fishery, and the potential biological consequences of these reductions at a relatively fine spatial scale. Therefore, we should not consider information on stock status as a transaction cost inhibiting a Coaseian transaction.

The other substantial source of transaction costs we may want to consider then are the costs of negotiating among the WCPFC members. There are roughly 14 nations actively participating in the WCPFC negotiations [@Hanich2012]. One can clearly imagine that this would impose substantial transaction costs for negotiating among these different countries. Given that informational transaction costs are unlikely to be the culprit, might negotiation costs be the reason that a Coaseian bargain has not already arisen as a solution to the Bigeye problem? Examining the status of other tuna stocks, including those managed by the WCPFC, this does not appear like a plausible explanation. For, example, both the Yellowtail (*Thunnus albacares*) and Skipjack stocks managed by the WCPFC have high biomass and low fishing rates. Only the Bigeye stocks are experiencing overfishing.

While the sample size is low (N = 4), this suggests that the negotiating costs of the WCPFC member states alone are not inhibiting the sustainable management of tuna stocks in the region. For the other tuna stocks, the member nations have been able to overcome the negotiation costs and set reasonable management targets. And, Bigeye is not the most valuable of the tuna stocks; its most unique characteristic is the bycatch connection between the Bigeye and Skipjack fisheries. So, while not definitive evidence, this suggests that transaction costs of negotiation are not inhibiting effective action in the WCPO tuna fisheries.

Together, this suggests that transaction costs may not be the prohibitive factor in the development of a Coaseian bargain to resolve. The other principal requirement for a Coaseian transaction is the presence of secure property rights. A Coaseian bargain depends on the ability for one party to pay for a good provided by the other party, and believe that that transaction will operate as planned. So, if I pay the neighboring rancher to keep her cattle off of my land, I can rest assured that this will in fact happen since a) I own my land and so have a thing to keep other things off of and b) she has ownership of the externality affecting my land and can mitigate it. The transaction begins to fall apart if my neighbor is only one of many sources of cattle rampaging across my fields, or if my neighbor cannot actually control her cattle.

In the case of Bigeye tuna, poor property rights appears to be the clearest reason for the lack of development of a Coaseian transaction to date. The Bigeye fishery is not currently rationalized. The fishery currently operates under a modified limited entry, with each individual member nation of the WCPFC providing regulations for entry into their permitted number of fishing days. In addition, there exist no clear demarcation between Skipjack and Bigeye interests. This makes the ability to identify clear parties who hold secure property rights very difficult to obtain.

Suppose a country or fleet with significant Bigeye interests could enter into an agreement with a Skipjack interest to reduce bycatch in exchange for payment. Without secure property rights, several problem arise. First, the Bigeye interests lack a reliable mechanism for ensuring they will get what they pay for. Ignoring contract enforcement costs, since the Bigeye stock is relatively open access in nature, Bigeye conserved by the Skipjack interest receiving the payment may simply be caught by another Skipjack interest. This greatly reduces the incentive of the Bigeye interest to pay for reductions, since it is unclear whether they will actually receive a reduction in Bigeye bycatch. At the same time, there are numerous Bigeye interests in the fishery. Unless they can all achieve coordination, there is a substantial risk that any improvements in the Bigeye stock will be captured or shared by a competing Bigeye interest. Together, these lack of secure property rights then greatly reduce the incentive of Bigeye interest to enter in a Coaseian bargain with the Skipjack interests.

## Assessment of Coaseian Potential

The available evidence suggests that the most significant reason that a Coaseian bargain has not already emerged in the Bigeye is the lack of clearly defined property rights. We have also seen though that lack of proportional benefits and costs under the status quo is one of the most significant barriers to the sustainability of the Bigeye stock. Therefore, we can suspect that a Coaseian bargain may be one of the most viable solutions to the Bigeye overfishing, but that this bargain may require strengthening of property rights to achieve.

Strengthening of property rights is not free. Establishing an reliably enforced ITQ throughout the region would likely incur substantial expenses. As such, it is worthwhile to consider beforehand the relative magnitude of benefits on the table. If the potential benefits to the Bigeye stock are equal to or greater than the costs required to be incurred by the Skipjack fishery in order to achieve those benefits, a bargain may be on the table. We can then consider whether sufficient surplus exists to account for the various costs that may be incurred in order to realistically make this transaction possible.

Our fist step then is to consider the magnitude of the potential surplus to the Bigeye interest resulting from reform of bycatch in the Skipjack fishery (and the associated costs of this bycatch reduction). The population modeled utilized for the assessment of Bigeye and Skipjack is highly detailed, incorporating age classes, quarterly time steps, and spatial considerations. Subsequent analyses on the specific management effects of bycatch reduction policies would likely require use of the stock assessment model, or a similar model of sufficient resolution. For early analyses though, we would prefer to avoid such complexity. For the following analyses we will make some simplifying assumptions to consider the potential magnitude of surplus from reforms.

We will ignore the complex population structure of tunas, and make calculations based on equilibrium assumptions based around reference points. Where needed, we will assume the population operates under Schaefer dynamics per

$$ N_{t+1} = N_{t}(1 - r(1 - \frac{N_{t}}{K})) - C_{t} $$

Which provide us will useful and simple derivations for reference points, namely

$$ B_{MSY} = K/2 $$

$$ F_{MSY} = r/2 $$

$$ MSY = rk/4 $$

an important implication of this model structure is that we can easily calculate the equilibrium (eq) stock status for any value of F/F~MSY~ as B/B~MSY~^eq^ = (2 - F/F~MSY~), and Catch/MSY as simply F/F~MSY~ X B/B~MSY~

Our goal however will be not to use any modeling, but rather to estimate the order of magnitude surplus available from reform, and consider what that means for the structure of a potential Coaseian bargain.

We will make calculations based on simplifying Schaefer assumptions, and make a number of other critical assumptions. We will not account for environmental drivers of stock status, meaning that management actions are exactly deterministic. We will not account for space, and assume that the population exists as one homogeneous blob. We will assume no fleet dynamics, meaning that we will not allow fishing effort to expand or contract as a function of expected fishing profits, or fishing costs to scale with effort. We will also not consider supply and demand, through which prices for Bigeye and Skipjack may fluctuate in response to the supply on the market. Lastly, we will assume that policies are perfectly implemented, and are enforced at zero cost.

Much of these initial back of the napkin results can be derived from considering Fig.2 and Fig.3. Let us assume that the objective of management is to achieve MSY. Maximum economic yield (MEY) would be a more appropriate objective from the perspective of the objectives of a Coaseian bargain, but we will cross that bridge when we get there. Let us consider Fig.2. We see that current B/B~MSY~ is ~1, F/F~MSY~ ~1.5, meaning that Catch/MSY is also 1.5. So, from our simplifying assumptions, we know right away that current catches are 1.5 times greater than can be sustained at equilibrium MSY. That means that catches at MSY will be 1/1.5 = 66.66% of current catches, meaning that future catches at MSY will need to be ~33% lower than current catches

Again, our goal for this exercise is to consider only a bycatch reduction policy, and not consider changes in catches by the Bigeye fleet itself. The Bigeye bycatch by the Skipjack fleet makes up ~50% of the current total Bigeye catch. Therefore, if we want to achieve MSY through bycatch alone, we would have to eliminate ~66% of the current Bigeye bycatch (33%/50%), which if we assume no improvements in Bigeye bycatch rates [which are already quite low, 1-3% @Hanich2012], and no spatial stratification in bycatch rates, would mean a 66% reduction in the Skipjack catch (since we assume that the amount of bigeye bycatch is just a proportion of the Skipjack catch) at B~MSY~.

How feasible might such a reduction be? The Skipjack fishery currently pulls in ~$1 billion in revenue. Assuming revenue is just a linear function of catch, a 66% reduction in catch will translate to a 66% reduction in revenue, or a loss of $666 million, using our simplifying assumptions. This is roughly equal to the ex-vessel value of Bigeye fishery today (~$600 million). In other words, if the Bigeye fishery were to attempt to enter into a Coaseian bargain with the Skipjack fishery today, it would cost roughly the entire ex-vessel revenue of the Bigeye fishery to pay off the Skipjack fishery to reduce bycatch enough to achieve Bigeye MSY (at equilibrium).

```{r, echo=F, warning=F}

bigeye_rev <- 6e8

skip_rev <- 1e9

```

Seeing as this ignores transaction costs and enforcement, for all practical intents and purposes, the cost of bycatch reduction would be greater than the current value of the fishery. In addition, under MSY there would be no room for expansion of Bigeye catches. So, the Bigeye fishery would be just as well off financially to maintain the status quo, and not pay to reduce Bigeye bycatch, if they are thinking relative to their current levels of revenue. However, this is clearly not the appropriate counter-factual. Current levels of catch are not sustainable. Therefore, we should consider whether the Coaseian bargain provides a net benefit relative to the expected catches under the status quo.

The equilibrium conditions under our simplified model are F/F~MSY~ = 1.5, B/B~MSY~ = 0.5, and Catch/MSY = 0.75. Seeing as Catch/MSY is 1.5, we expect future catches at equilibrium to be 50% of current catches (0.75/1.5). We would then expect future revenues to be ~50% of current revenues, or $300 million. Looking at the Skipjack scenario, current levels of Skipjack mortality and catch appear to be approximately sustainable (Figure.2), meaning that the Skipjack fleet might expect to catch at least as much as it currently does today, and therefore expect a stream of bycatch reduction payments roughly equal to their current value, or $666 million per year, to reduce bycatch levels to the amount required to prevent Bigeye overfishing. We also know that at MSY, this cost is roughly equivalent to the ex-vessel revenues of the Bigeye fishery at MSY, since revenues today will roughly equal revenues at MSY under our assumptions. So, the Bigeye negotiators roughly would consider two scenarios. They could either expect revenues of $600 million per year and payments of ~$666 million per year, and so a net benefit of ~$0, or maintain the status quo for free, and expect $300e6 in revenues. The status quo is preferable, and a bargain does not appear to be on the table, at least from an MSY-or-nothing perspective. In other words, under these assumptions there does not appear to be a Coaseian bargain that is capable of completely stopping overfishing of Bigeye through bycatch reductions.

Clearly this is a huge simplification, at the very least we could easily actually use our model to estimate the discounted NPV of different scenarios. For example, there may well be a bargain on the table that reduces Bigeye bycatch somewhat, i.e. a level of bycatch reduction that provides greater benefits to the Bigeye fleet than would occur under the status quo, but not enough to completely prevent overfishing. From our calculations, the maximum willingness to pay by the Bigeye fleet is ~$300 million. So, they may be willing to pay to be in a less overfished state in the future, but Bigeye cannot afford to completely prevent overfishing through payments to the Skipjack fleet. But I do not believe that explicitly analyzing dynamics will change the overall result that based on the rough orders of magnitude of costs and benefits to Bigeye and Skipjack, a Coaseian bargain is not a viable strategy for achieving a reduction in Bigeye bycatch sufficient to prevent Bigeye overfishing.

```{r, echo=F}
# ![Catch composition by gear type for Bigeye tuna in the WCPO (Harley et al. 2014)](bigeye_catch_plot.tiff)
#
# ![Catch composition by gear type for Skipjack tuna in the WCPO (Rice et al. 2014)](skipjack_catch_plot.tiff)
```

![Kobe plot for Bigeye tuna in the WCPO (Harley et al. 2014)](bigeye_kobe_plot.tiff)

![Kobe plot for Skipjack tuna in the WCPO (Rice et al. 2014)](skipjack_kobe_plot.tiff)

## Alternative Benefits from a Coaseian Bargain

These preliminary calculations are obviously not accurate, but suggest that a Coaseian bargain may not solve Bigeye overfishing simply based on the gross landed value of reform. Might alternative visions of mechanisms and effects of bycatch reduction change this story?

### Value-Per-Recruit

We assume in our simplified calculations that revenues are simply a linear function of biomass. In reality though, different sizes and qualities of bigeye fetch far different prices. Sashimi grade Bigeye can fetch nearly $10/kg, while canned juvenile bigeye caught as bycatch sells for $1.5/kg [@Bell2015]. So, we can already see several benefits to bigeye bycatch reduction not captured in our simple calculations. First, under the status quo we will be both recruitment and growth overfishing the population, meaning that we are both reducing the yield per recruit and the spawners per recruit.

Reducing bycatch of juveniles, and allowing recruited Bigeye to reach larger sizes before being caught by the more selective long-line fleet will right away increase the yield-per-recruit. This should mean that the Bigeye fleet could catch fewer individuals but maintain or increase the landed weight, potentially reducing costs [see @Sun2015 for a Bigeye specific example]. So, even ignoring the price difference related to size, the Bigeye fleet may be made better off from bycatch reduction than would be expected by the biomass dynamics approach outlined above. Once we factor in the nearly 10x increase in price for larger Bigeye on the sashimi market, into something like a value-per-recruit approach, the economic benefits of Bigeye reform may become much larger. This may make a Coaseian bargain more feasible than our first analysis suggests.

In addition, we have considered revenues in these simple calculations. If the relative cost to revenue ratios of the Bigeye and Skipjack fisheries are similar, this should not matter much. But, if fishing costs are substantially greater or lower in one fishery or the other the payments required to achieve a Coaseian solution may change. Kompas et al. [-@Kompas2010] suggest potentially different costs among the two industries, but do not report comparable cost units so it is difficult to say if Bigeye or Skipjack are cheaper to catch. Consider though if Skipjack is much more expensive to fish than Bigeye. The required payments for a Coaseian bargain will depend on Skipjack's perceived stream of net benefits, aka profits. Therefore, we may be unduly penalizing the ability of the bargain to take place by charging the Bigeye interests by revenue, where in reality the profits in the fishery may be much lower, and perhaps closer in size to the profits in the Bigeye fishery.

### Improved Bycatch Reduction

The value-per-recruit strategy outlined above may substantially alter the perceived economic benefits to the Bigeye fleet of paying for bycatch reduction. An alternative strategy though would be to see if we could make those payments cheaper. Under our simple assumptions, we considered the Bigeye bycatch as being homogeneously distributed across the Skipjack catch, i.e all Skipjack pulls have a 1-3% bycatch rate. One strategy then might be to attempt to reduce this bycatch rate. This seems like a daunting task though. The Bigeye bycatch rate is already very low. We do not have a scenario like shrimp where bycatch rates are nearly 80-90% of the catch, which may in turn provide ample space for improvements. Technological fixes such as a two-stage FAD used to separate Bigeye from Skipjack may be able to reduce bycatch some, but it seems unlikely to provide a substantial reduction from the already low rates.

Another possibility here though is to identify hot-spots of Bigeye bycatch. If Bigeye bycatch is not evenly distributed, but is concentrated in pockets of relatively low and high bycatch, then bycatch reduction may in fact by much cheaper. A quick comparison of the spatial distribution of catch in the Skipjack and Bigeye fisheries shows that Skipjack fishing is concentrated in the Western Pacific, particularly North-East of Papua New Guinea. Conversely, much of the Bigeye bycatch is concentrated in the Central Pacific, east of Kiribati. This suggest then that targeted bycatch reduction in specific areas, namely in the Central Pacific, may be able to achieve substantial amounts of Bigeye bycatch reduction at much lower cost, in terms of landings, to the overall Skipjack fishery. Consideration of these spatial dimensions of bycatch appears the most viable avenue for increasing the viability of a Coaseian bargain to prevent Bigeye overfishing. These ideas are supported by [@Little2015; @Sibert2012].

### Critical Costs

So far we have minimized consideration of costs, and even without cost, have shown that a Coaseian bargain is not particularly viable strategy. However, taking into account space and value-per-recruit may dramatically change the benefit side of the equation. It is only fair then that we also consider key costs that we will need to consider through this analysis.

#### Enforcement costs

Mention tuna management to just about anyone with even a rudimentary knowledge of the system, and the question of enforcement quickly rears its ugly head. So far, we have assumed that the Bigeye interests are completely confident that their payments to Skipjack will achieve the agreed upon level of bycatch reduction. For large pelagic fisheries though, this is likely unreasonable. Given the diverse number of players involved, and the relative difficulty of detecting and enforcing poaching, it would be challenging to ensure that the Skipjack interests paid to reduce bycatch are in fact doing what they said, and that illegal Skipjack operations do not simply capture any reductions in bycatch achieved through legal channels.

It will be critical to attempt to at least roughly quantify the associated enforcement costs of specific policy interventions we explore to reduce Bigeye bycatch. For example, we could attempt to consider the price-per-km^2^ of enforcement of spatial Skipjack fishing closures related to Bigeye bycatch prevention. These costs will then have to be factored into the relative costs and benefits of any proposed Coaseian bargain.

#### Unitization Problem

We have also ignored transaction costs so far. We have reason to think that the transaction costs of getting all the players in the same room is not insurmountable. But, the transaction costs of negotiating a Coaseian payment may not be trivial. So far, we have considered the Bigeye and Skipjack interests as two individual players, representing the aggregate interests of each fleet. In reality, each of these fisheries is comprised of a number of different fleets, with potentially heterogeneous distribution of Skipjack benefits and bigeye burdens. A Coaseian solution then will have to involve coalitions of Bigeye interests paying coalitions of Skipjack interests. In many ways this is a similar problem to the development of oil field unitization [@Wiggins1985; @Libecap1999]. Bigeye interests left out of a negotiation may reap benefits without payment, reducing the incentive of involved Bigeye interests to pay for conservation. Or, omitted Bigeye interests may simply expand effort in response to conservation outcomes negotiated by the involved Bigeye interests. On the other side of the table, if all the relevant Skipjack interests are not included, omitted Skipjack interests may simply fill any gaps in bycatch created by the agreement, for example by traveling to and fishing in areas closed to Skipjack fishing by the involved Skipjack interests.

The willingness of each interest group to participate will then depend not only on the aggregate costs and benefits, but the relevant distribution of these costs and benefits. So, Kiribati may be far less inclined to participate in an agreement that provides most of its benefits to Japan, unless the correct mechanisms are in place to ensure that they are compensated proportionally. While assessing the full spatial-temporal dynamics of Bigeye bycatch reduction plans will likely be outside of the scope of this paper, we will need to at least consider the rough degree of heterogeneity in stakeholders and the spatial distribution of costs and benefits, and attempt to model the formation of coalitions.

#### Property rights

Lastly, and related to enforcement costs, we have not considered the presence or cost of property rights. As was previously mentioned, the Bigeye and Skipjack fisheries are not rationalized. This inhibits the ability of an effective Coaseian bargain to form. The Skipjack interests do not actually own rights to the fishery that they can sell in exchange for payments for bycatch reduction. So, in theory new entrants to the fishery, or Skipjack interests not involved in a negotiation could simply decide to scoop up any conserved Skipjack and associated Bigeye. However, loose property rights do exist to tunas within EEZs. So, Bigeye interest could pay countries to restrict access to fishing within their EEZs conditional on adopting requested Bigeye protective measures, or to simply reduce the number of fished vessel days that a country sells. Strengthening this property enough to create sufficient confidence for a Coaseian transaction will likely require investment in enforcement technology.

The other problem though is that both Skipjack and Bigeye move both across EEZs and out into international waters. Here there is clearly no property right; individual countries or fleets could commit to changes in practices in international waters, but there would be very little stopping anyone not interested in joining an agreement to fish however they wanted out there. It is far less clear how to resolve the property right challenge in the high seas. One strategy for this paper could be to simply write the high seas off and attempt to estimate the amount of benefits that could be achieved from working inside EEZs alone. Another strategy could be to attempt to rationalize the processing sector, and as part of that process convince the processing sector to only accept, or pay a premium for, tuna certified to be caught in accordance with agreed upon practices (in exchange for payment by Bigeye interests).

## Conclusions

That the overfishing of Bigeye persists is perhaps then not a great mystery. The highly migratory nature of tuna can easily create an incentive to overfish, in the manner predicted by Hardin and Gordon [-@Gordon1954]. Incentives are sufficiently aligned to promote cooperation and succesful management in many tuna species, but Bigeye presents a special challenge, due to the imbalance of costs and benefits between the Skipjack and Bigeye fisheries. Our initial results provide some evidence of why a Coaseian bargaining solution has not yet arisen naturally as a solution: property rights are weak, and the relative balance of costs and benefits is poor.

However, this does not mean that a Coaseian bargain does not hold potential. The imbalance of costs and benefits seems like the clearest impediment to the conservation of Bigeye, and a Coaseian solution provides the clearest path to resolving that type of problem. Initial results show that based solely on gross landed revenue a Coaseian solution, while potentially capable of reducing fishing pressure, may not be able to completely prevent overfishing. However, further analysis incorporating value-per-recruit analyses and spatial heterogeneity in bycatch rates may substantially change the balance of costs and benefits for this proposed transaction.

Broadly, this system of analysis allows us to more rigorously consider why we persist in seeing a seemingly irrational problem. By not simply writing off a "undesirable" result as an externality, but rather considering the incentive structures among participants, the root causes, and potential solutions, to environmental problems can be more clearly identified.

## Works Cited
